Composable Generalized Consensus

### 2016-01-07 paper/abstract4.tex
work on the abstract: shortening of first paragraph (problem statement).

State-Machine Replication (SMR) algorithms such as Paxos are notoriously hard to
understand, let alone to devise. Moreover, there is no practical way to reuse
and optimize existing SMR algorithms, therefore the cost of creating a new SMR
algorithm is high.

To lower this cost, we present a framework for building SMR algorithms out of
independent and reusable SMR modules. A module is an SMR algorithm that can
abort and pass the baton to another module, allowing to dynamically switch
between modules. Our composition theorem ensures that the composition of any
number of modules satisfying Composable Generalized Consensus (CGC), our
correctness condition for modules, is a correct SMR algorithm.

To help design new modules in practice, we propose TLA$^+$ specifications
of CGC and of two abstract types of modules, fast rounds and conservative
rounds, each providing a template to devise new SMR modules with the help of the
TLA$^+$ tools. We show that several well-known SMR algorithms can be modified to
implement fast or conservative rounds, therefore enabling their composition to
obtain a single versatile SMR algorithm.

>>>>

%State-Machine Replication (SMR) algorithms such as Paxos are notoriously hard to
%understand, let alone to devise. Moreover, there is no practical way to reuse
%and optimize existing SMR algorithms, therefore the cost of creating a new SMR
%algorithm is high.

State-Machine Replication (SMR) algorithms are notoriously hard to understand
and devising new and more performant SMR algorithms is costly. To lower this
cost, we present a framework for building SMR algorithms out of independent
and reusable modules. A module is an SMR algorithm that can abort and pass
the baton to another module, allowing to dynamically switch between modules.
Our composition theorem ensures that the composition of any number of modules
satisfying Composable Generalized Consensus (CGC), our correctness condition for
modules, is a correct SMR algorithm.

To help design new modules in practice, we propose TLA$^+$ specifications
of CGC and of two abstract types of modules, fast rounds and conservative
rounds, each providing a template to devise new modules with the help of the
TLA$^+$ tools. We show that several well-known SMR algorithms can be modified to
implement fast or conservative rounds, therefore enabling their composition to
obtain a single versatile SMR algorithm.
